Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-08-03 02_paper/02_study/paper_methods.Rmd
Update paper_methods.Rmd

Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson & Weinstein, 2006; Kounin, 2006). Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom. This ability is referred to as classroom professional vision (Goodwin, 1994; Sherin, 2007). The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (“noticing”) and applying knowledge to draw appropriate conclusions in these situations (“knowledge-based reasoning”; Seidel & Stürmer, 2014). Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students’ learning time and minimize classroom interruptions. According to Kounin (2006), these important classroom management strategies are called “withitness” and “overlapping” and can be summarized under the concept of monitoring (Gold & Holodynski, 2017). Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff et al., 2017). Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, “[…] whereas only a few studies have focused on the basal process of noticing, i.e. the recognition of possible disturbing situations” (Grub et al., 2020, p.75). Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (Lachner et al., 2016; Wolff et al., 2016).

@@

Competence is a common term in everyday school life. In most cases, it refers to the acquisition of competencies by students and how to promote them and make them effective. In the same way, the term competence can be applied to teachers. Teachers have to be competent in things such as teaching, educating, evaluating or innovating. Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig & Rauch, 2008). They replace the rigid canon of knowledge that defined professional qualification for generations. In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.). To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf. Klieme et al., 2008, p. 4). In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.

@@

The term "professional competence" is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation." (cf. Epstein & Hundert, 2002; cited in Kunter et al. 2013, p. 807). Several studies could prove that this idea can be successfully transferred to the teaching profession (cf. Goodmann et al., 2008; Oster, Achtenhagen & Renold, 2006; Tannenbaum & Rosenfeld, 1994; cited in Kunter et al., 2013, p. 807). Accordingly, a quality standard can be applied to assess the quality of a teacher. This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano & Pickering, 2003). Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher. Research has shown that this component can even offset the influence of an ineffective school setting (Marzano et al., 2003). This effect places teachers at the center of ensuring effective teaching and learning and underscores the importance of professional competence in this career field.

@@

However, lessons, and specifically classroom disruptions, are unpredictable as well as multifaceted and require a high level of expertise and competence on the part of the teacher to handle. This trained handling, as described above, can be summarized under the aspect of professional competence. It is expressed, among other things, in knowledge about classroom management (Grub, Biermann & Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.

Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, van den Bogert, Jarodzka & Boshuizen, 2015). Marzano et al.'s (2003) research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching. In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching (Wolff et al., 2015). Therefore, it is often referred to as the central variable of successful teaching (Helmke & Helmke, 2015). Good classroom management is thus the prerequisite for learning to take place (Wolff et al., 2015). While the term suggests that it is mainly about rituals, rules, or measures that are meant to maintain order within the classroom, it is about much more than these two components.

@@

Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf. Wolff et al., 2015, p. 71). These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.). If these very skills are well-developed, they guarantee a smooth and trouble-free course of instruction. This is crucial to maximize students' active learning time (Helmke & Helmke, 2015). It, in turn, has been shown to correlate positively with achievement growth and learning interest in a class (Helmke, 2008), placing effective classroom management at the center of empirical research. In principle, these skills can be developed in the course of teaching education, as well as subsequent professional experience, which is why they constitute an essential component of teacher expertise (Wolff et al., 2015).

>>>>

Managing classroom disruptions is a crucial aspect of effective classroom management [@evertson2006classroom; @kounin2006techniken]. Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom. This ability is referred to as classroom professional vision [@goodwin2015 professional; @sherin2007development]. The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (“noticing”) and applying knowledge to draw appropriate conclusions in these situations [“knowledge-based reasoning”; @seidel2014modeling]. Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students’ learning time and minimize classroom interruptions. According to @kounin2006techniken, these important classroom management strategies are called “withitness” and “overlapping” and can be summarized under the concept of monitoring [@gold2017using]. Learning to develop such classroom management skills is a demanding and complex task for student teachers [@wolff2016teacher]. Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, “[…] whereas only a few studies have focused on the basal process of noticing, i.e. the recognition of possible disturbing situations” [@grub2020processp, p.75]. Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions [@lachner2016makes; @wolff2016teacher].

@@

Competence is a common term in everyday school life. In most cases, it refers to the acquisition of competencies by students and how to promote them and make them effective. In the same way, the term competence can be applied to teachers. Teachers have to be competent in things such as teaching, educating, evaluating or innovating. Therefore, competencies form an important and practical contribution in current educational research and teacher education [@klieme2008concept]. They replace the rigid canon of knowledge that defined professional qualification for generations. In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.). To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education [cf. @klieme2008concept, p. 4]. In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.

@@

The term "professional competence" is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation." [cf. @epstein2002defining; cited in Kunter et al. 2013, p. 807]. Several studies could prove that this idea can be successfully transferred to the teaching profession [cf. Goodmann et al., 2008; @oser2006competence, Achtenhagen & Renold, 2006; Tannenbaum & Rosenfeld, 1994; cited in Kunter et al., 2013, p. 807]. Accordingly, a quality standard can be applied to assess the quality of a teacher. This quality is elementary in the school context because the teacher factor most influences student learning [@marzano2003classroom]. Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher. Research has shown that this component can even offset the influence of an ineffective school setting [@marzano2003classroom]. This effect places teachers at the center of ensuring effective teaching and learning and underscores the importance of professional competence in this career field.

@@

However, lessons, and specifically classroom disruptions, are unpredictable as well as multifaceted and require a high level of expertise and competence on the part of the teacher to handle. This trained handling, as described above, can be summarized under the aspect of professional competence. It is expressed, among other things, in knowledge about classroom management [@grub2020process] and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.

Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction [@wolff2015keeping]. @marzano2003classroom research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching. In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching [@wolff2015keeping]. Therefore, it is often referred to as the central variable of successful teaching (Helmke & Helmke, 2015). Good classroom management is thus the prerequisite for learning to take place [@wolff2015keeping]. While the term suggests that it is mainly about rituals, rules, or measures that are meant to maintain order within the classroom, it is about much more than these two components.

@@

Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge [cf. @wolff2015keeping, p. 71]. These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.). If these very skills are well-developed, they guarantee a smooth and trouble-free course of instruction. This is crucial to maximize students' active learning time (Helmke & Helmke, 2015). It, in turn, has been shown to correlate positively with achievement growth and learning interest in a class (Helmke, 2008), placing effective classroom management at the center of empirical research. In principle, these skills can be developed in the course of teaching education, as well as subsequent professional experience, which is why they constitute an essential component of teacher expertise [@wolff2015keeping].
